---
title: "R Notebook"
output: html_notebook
---
##Step o library and dependency
```{r}
install.packages("tm")
install.packages("SnowballC")
library(tm)
```

##Step 1 Load Data
```{r}
df <- read.csv(file = "C:/Users/User/Documents/UNITS/Magistrale/Primo Anno/1°semestre/Machine Learning/SvevoLetters/carteggiosvevo3.csv", sep = ";", header = TRUE)
head(df)
dimensions <- dim(df)
rows <- dimensions[1]
columns <- dimensions[2]
```
##Step 2 pre processing
```{r}
LetterCorpussection <- table(df[,2])
Sections <- dim(LetterCorpussection)
Sections
SectionNames <-levels(factor(df$corpus))
SectionNames
LetterCorpussection

  for (k in 1:45){
    SectionNames[k]
    for(i in 1:rows){
    if (df[i,2] == SectionNames[k]){
      data <- df[i, c("sender","recipient")]
      print(data)
    }
      
    }
  }
  
```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
