---
title: "R Notebook"
output: html_notebook
---
##Step o library and dependency
```{r}
# loading the required packages
install.packages("dplyr")
install.packages("tidyr")
install.packages("textreg")
install.packages("tm")
install.packages("writexl")
install.packages("corpus")
install.packages("e1071")
install.packages("wordcloud2")
install.packages("caret")
install.packages("tidytext")
install.packages("tokenizers")
install.packages("textclean")

library(textclean)
library(dplyr)
library(tidyr)
library(textreg)
library(tm)
library(writexl)
library(corpus)
library(e1071)
library(wordcloud2)
library(caret)
library(tidytext)
library(tokenizers)
```

##Step 1 Load Data
```{r}
df <- read.csv(file = "C:/Users/User/Documents/UNITS/Magistrale/Primo Anno/1°semestre/Machine Learning/SvevoLetters/carteggiosvevo3.csv", sep = ";", header = TRUE)
head(df)
dimensions <- dim(df)
rows <- dimensions[1]
columns <- dimensions[2]
```
##Step 2 pre processing
```{r}
LetterCorpusSection <- table(df[,2])
Sections <- dim(LetterCorpusSection)
Sections
SectionNames <-levels(factor(df$corpus))
SectionNames
```
##Updatying an eglish list to compute the stemming
```{r}
stem_hunspell <- function(term) {
    # look up the term in the dictionary
    stems <- hunspell::hunspell_stem(term)[[1]]

    if (length(stems) == 0) { # if there are no stems, use the original term
        stem <- term
    } else { # if there are multiple stems, use the last one
        stem <- stems[[length(stems)]]
    }

    stem
}

```

##New section in which we perform preprocessing
```{r}
#clean the text data
library(stringr)
stop_words <- c(stopwords("en"),stopwords("italian"),stopwords("german"))
df_clean <- df %>% 
   mutate(text_clean = text %>% 
             str_replace_all("[0-9]", " ") %>% 
             str_replace_all("[-|]", " ") %>% 
             tolower() %>% 
             str_replace_all("[[:punct:]]", " ") %>% 
             str_replace_all(" dr ", " doctor ") %>% 
             str_replace_all(" s ", " ") %>%  
             str_squish()%>%
            str_trim()
             
          )
# converting date into date object
gsub("00","01",df_clean$date)# forunknown month or year we assume it is the first month and first year
df_clean$date <- as.Date(df_clean$date,tryFormats = c("%d-%m-%Y", "%d/%m/%Y"))
# verifying
glimpse(df_clean)
```

##we count the number of words in each document 
```{r}
documents_length <- sapply(strsplit(df_clean$text, " "), length)
documents_length

documents_length %>% 
   summary()
```

##create a copus composed only by the text data
```{r}
stem_hunspell <- function(term) {
    # look up the term in the dictionary
    stems <- hunspell_stem(term)[[1]]
    
    if (length(stems) == 0) { # if there are no stems, use the original term
        stem <- term
    } else { # if there are multiple stems, use the last one
        stem <- stems[[length(stems)]]
    }
    return(stem)
}

news_term <- df_clean %>% 
   unnest_tokens(output = "word", input = text_clean) %>% 
   anti_join(stop_words)  %>% 
   mutate(word = ifelse(word == "positive", "positives", word),
          word = text_tokens(word, stemmer = stem_hunspell) %>% as.character() ) %>% 
   drop_na(word) %>% 
   count(V1, word)

```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
